Non-Vertical Cultural Transmission and the\\ Evolution of Cooperation

### 2020-08-28 ms/main.tex
Result 1 describe what happen if T_A = T_B

Non-vertical cultural transmission may be either viewed as horizontal or oblique: horizontal transmission occurs between individuals from the same generation, while oblique transmission occurs  to  offspring from the generation to which their parents belong. 
Evolution under either of these transmission models  can be be more rapid than under pure vertical transmission~\citep{cavalli1981cultural,lycett2008questions,ram2018evolution}.
\citet{lewin2017microbes} and \citet{lewin2020rock–paper–scissors} have demonstrated that non-vertical transmission, mediated by microbes that manipulate their host's behavior, can help to explain the evolution of cooperative behavior. Some of their analysis can be applied to cultural transmission, because models of cultural transmission are mathematically similar to those for transmission of infectious diseases~\citep{cavalli1981cultural}.
Importantly, their results depended on non-vertical transmission of the cooperation-determining microbes.

@@

Therefore, in the absence of vertical transmission, selection plays no role in the evolution of cooperation. Hence, cooperation will evolve if the cooperator phenotype has a horizontal transmission bias (see~{\autoref{fig:results}c).

>>>>

Non-vertical cultural transmission may be either viewed as horizontal or oblique: horizontal transmission occurs between individuals from the same generation, while oblique transmission occurs  to  offspring from the generation to which their parents belong. 
Evolution under either of these transmission models  can be be more rapid than under pure vertical transmission~\citep{cavalli1981cultural,lycett2008questions,ram2018evolution}.
\citet{lewin2017microbes} and \citet{lewin2020rockpaperscissors} have demonstrated that non-vertical transmission, mediated by microbes that manipulate their host's behavior, can help to explain the evolution of cooperative behavior. Some of their analysis can be applied to cultural transmission, because models of cultural transmission are mathematically similar to those for transmission of infectious diseases~\citep{cavalli1981cultural}.
Importantly, their results depended on non-vertical transmission of the cooperation-determining microbes.

@@

If $T_A = T_B$, then $p'=p$ and the population is static.
Therefore, in the absence of vertical transmission, selection plays no role in the evolution of cooperation. Hence, cooperation will evolve if the cooperator phenotype has a horizontal transmission bias (see~{\autoref{fig:results}c).
